A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2020-12-05 stashed/doc/paper1-submission/paper5-adjusted.tex
moving to a committed stash to avoid clashes while restoring functionality

\caption{Exemplified input trees (a-b) and taxonomy tree (c) from Fig. \ref{fig:cleaned-phylo-example}.
Taxon E in (a) is exemplified by E1. Pruned taxa are E2, F2, and D. The
taxa E and F are retained as monotypic taxa in the pruned taxonomy
$\protect\prunedTaxonomy$. The red
edge in the pruned taxonomy tree is an uncontested higher taxon in
the exemplified taxonomy (as explained in section \ref{subsec:Subproblem-decomposition})}
\label{fig:exemplify-example}
\end{figure}

@@

\caption{Subproblems \emph{ABCD} and \emph{root} generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig7}

@@

\caption{Solutions to subproblem \emph{ABCD} and subproblem \emph{root} depicted in Fig. \ref{fig:subproblems-example}.}
\label{fig:subproblem-solutions.}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{Fig10.pdf}
\par\end{centering}
\caption{Grafted solution produced from the subproblems from
Fig. \ref{fig:subproblem-solutions.} and which is the 
backbone onto which taxa that are not included in any phylogeny
will be placed.
In a real analysis, the tips shown as E and F here
would be monotypic taxa (with children E1 and F1, respectively)
from the trivial subproblems that were omitted from from Fig. \ref{fig:subproblems-example}.}
\label{fig:grafted-solution}
\end{figure}

@@

\caption{\label{fig:displayed-annotations}The relationship of edges in summary
tree $\protect\summaryTree$ (b) to edges in the input tree $T_{1}$
(a). Only edges of $\protect\summaryTree$ that are present in the
induced tree $\protect\summaryTree(1)$ are represented by JSON annotations
(d). Taxon names are here suppressed in favor of OTT IDs, and edges
are referenced via their tipward nodes. Edges in $\protect\summaryTree(1)$
that correspond to terminal edges of $T_{1}$ are orange; edges of
$\protect\summaryTree(1)$ that are supported by edges of $T_{1}$
are blue; where multiple edges of $\protect\summaryTree(1)$ correspond
to the same edge of $T_{1}$ they are green. There is no conflict
in this example. Also, if this were output from propinquity, then
each internal node of $\protect\summaryTree$ would be supported by
other inputs trees that are not shown here. }
\end{figure}

>>>>

\caption{Exemplified input trees (a-b) and pruned taxonomy tree (c) from Fig. \ref{fig:cleaned-phylo-example}.
Taxon E in the first input tree is exemplified by E1 in (a). Pruned taxa are E2, F2, and D. The
taxa E and F are retained as monotypic taxa in the pruned taxonomy. The red
edge in the pruned taxonomy tree is an uncontested higher taxon in
the exemplified taxonomy (as explained in section \ref{subsec:Subproblem-decomposition})}
\label{fig:exemplify-example}
\end{figure}

@@

\caption{Subproblems (a) \emph{ABCD} and (b) \emph{root} generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig7}

@@

\caption{Solutions to (a) subproblem \emph{ABCD} and (b) subproblem \emph{root} depicted in Fig. \ref{fig:subproblems-example}.}
\label{fig:subproblem-solutions.}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{Fig10.pdf}
\par\end{centering}
\caption{Grafted solution produced from the subproblems from
Fig. \ref{fig:subproblem-solutions.} and which is the 
backbone onto which taxa that are not included in any phylogeny
will be placed.}
\label{fig:grafted-solution}
\end{figure}

@@

\caption{\label{fig:displayed-annotations}The relationship of edges in summary
tree $\protect\summaryTree$ in panel (b) to edges in the input tree $T_{1}$ named ``tree1'' in panel
(a). Only edges of $\protect\summaryTree$ that are present in the
induced tree $\protect\summaryTree(1)$ in panel (c) are represented by JSON annotations
in panel (d). Taxon names are here suppressed in favor of OTT IDs, and edges
are referenced via their tipward nodes. Edges in $\protect\summaryTree(1)$
that correspond to terminal edges of $T_{1}$ are orange; edges of
$\protect\summaryTree(1)$ that are supported by edges of $T_{1}$
are blue; where multiple edges of $\protect\summaryTree(1)$ correspond
to the same edge of $T_{1}$ they are green. There is no conflict
in this example. Also, if this were output from propinquity, then
each internal node of $\protect\summaryTree$ would be supported by
other inputs trees that are not shown here. }
\end{figure}
